---
title: "1.DataSimulation"
author: "Joukje Willemsen"
date: "13-05-2020"
output: html_document
---

In this document the current controls and the corresponding experimental datasets for the scenarios referred to as A, B, C1-3 and D1-3 in the article are simulated and stored.

Please note that:

Data11 = Scenario A

Data12 = Scenario C1

Data13 = Scenario C2

Data14 = Scenario C3

Data21 = Scenario B

Data22 = Scenario D1

Data23 = Scenario D2

Data24 = Scenario D3

#Load packages
```{r}
library(dplyr)
library(survival)
```

#Load estimated parameters, the calculated samplesize & HR from 0.DataPreperation
```{r}
load("0.DataPreperation_output/0.Parameters.RData") #load parameters Weibull distribution
load("0.DataPreperation_output/0.SampleSize.RData") #load the calculated sample size
load("0.DataPreperation_output/0.HRcont_exp.Rdata") #load HR used to calculate samplesize
```

#Function to simulate Time Until Mortality
```{r}
TimeUntilMortality <- function(shapeparameter = parameters$shape,scaleparameter,treatmenteffect = HR,allocation,sdrandomeffectcluster, Tmax = 548, pcont = 0.5, N = SampleSize)
  
  {
#Make 3 groups:
# 0 controlgroup
# 1 exp group where HR = HR
# 2 exp group where HR = 1
Data <- as.data.frame(c(rep.int(0, pcont*N), rep.int(1, (1-pcont)*N),rep.int(2, (1-pcont)*N)))
colnames(Data)<-"allocation"

#indicate whether an effect should be simulated (only when allocation = 1)
Data$effectgroup <- if_else(Data$allocation == 1, 1, 0) 

#Generate random effect cluster
Data$randomeffectcluster <- rnorm(1, mean = 0, sd = sdrandomeffectcluster)

#Time until mortality
Data$TUM <- Data %>% 
               nrow() %>% 
               rweibull(shapeparameter,scaleparameter*exp(-(Data$effectgroup*treatmenteffect+
                 Data$randomeffectcluster)/shapeparameter))

#Add censoring indicator
Data$censoring <- ifelse(Data$TUM>Tmax, yes = 1, no = 0)
Data$survivalcensored <- ifelse(Data$TUM>Tmax, yes = Tmax, no = Data$TUM)

#Add status indicator
Data$StatusIndicator <- ifelse(Data$TUM>Tmax, yes=0, no = 1) 

return(Data)
}
```

#Input for the different scenarios
Set different parameters (see researchreport)
```{r}
shapeparameter = parameters$shape
scaleparameter = c(parameters$scale, parameters$scale+100) #Corresponding to an effectsize of HR=1 and HR=1.128719
treatmenteffect = HR #the HR used in 0.DataPreperation to calculate the sample size
sdrandomeffectcluster = c(0, 0.1, 0.2, 0.4)
```


#Simulate datasets
```{r}
set.seed(123)

Data11 <- TimeUntilMortality(scaleparameter = scaleparameter[1], sdrandomeffectcluster = sdrandomeffectcluster[1])

Data12 <- TimeUntilMortality(scaleparameter = scaleparameter[1], sdrandomeffectcluster = sdrandomeffectcluster[2])

Data13 <- TimeUntilMortality(scaleparameter = scaleparameter[1], sdrandomeffectcluster = sdrandomeffectcluster[3])

Data14 <- TimeUntilMortality(scaleparameter = scaleparameter[1], sdrandomeffectcluster = sdrandomeffectcluster[4])

Data21 <- TimeUntilMortality(scaleparameter = scaleparameter[2], sdrandomeffectcluster = sdrandomeffectcluster[1])

Data22 <- TimeUntilMortality(scaleparameter = scaleparameter[2], sdrandomeffectcluster = sdrandomeffectcluster[2])

Data23 <- TimeUntilMortality(scaleparameter = scaleparameter[2], sdrandomeffectcluster = sdrandomeffectcluster[3])

Data24 <- TimeUntilMortality(scaleparameter = scaleparameter[2], sdrandomeffectcluster = sdrandomeffectcluster[4])
```


#Function to create 1000 replications
```{r}
replicatedatasets <- function(scaleparameter, sdrandomeffectcluster, nrep = 1000){
  
namedata <- list()
for(i in 1:nrep){
  tmp  <- TimeUntilMortality(scaleparameter = scaleparameter, sdrandomeffectcluster = sdrandomeffectcluster, pcont = 0.5, N = SampleSize, treatmenteffect = HR) 
  name <- paste('iteration:',i,sep='')
  namedata[[name]] <- tmp
}
return(namedata)
}
```


#Replicate the proces of generating the datasets 1000 times and store them in a list
```{r}
set.seed(123)

Data11_list <- replicatedatasets(scaleparameter = scaleparameter[1], sdrandomeffectcluster = sdrandomeffectcluster[1])

set.seed(123)

Data12_list <- replicatedatasets(scaleparameter = scaleparameter[1], sdrandomeffectcluster = sdrandomeffectcluster[2])

set.seed(123)

Data13_list <- replicatedatasets(scaleparameter = scaleparameter[1], sdrandomeffectcluster = sdrandomeffectcluster[3])

set.seed(123)

Data14_list <- replicatedatasets(scaleparameter = scaleparameter[1], sdrandomeffectcluster = sdrandomeffectcluster[4])

set.seed(123)

Data21_list <- replicatedatasets(scaleparameter = scaleparameter[2], sdrandomeffectcluster = sdrandomeffectcluster[1])

set.seed(123)

Data22_list <- replicatedatasets(scaleparameter = scaleparameter[2], sdrandomeffectcluster = sdrandomeffectcluster[2])

set.seed(123)

Data23_list <- replicatedatasets(scaleparameter = scaleparameter[2], sdrandomeffectcluster = sdrandomeffectcluster[3])

set.seed(123)

Data24_list <- replicatedatasets(scaleparameter = scaleparameter[2], sdrandomeffectcluster = sdrandomeffectcluster[4])
```

#Store the lists in one big list
```{r}
ALLdata <- list(Data11_list, Data12_list, Data13_list, Data14_list,
                    Data21_list, Data22_list, Data23_list, Data24_list)
```

#Store a subset with only controls and only experimental (both with HR=1 and HR=0.5)
```{r}
Hcontrol <- list()
for (a in 1:8){
  Hcontrol[[a]]<-list()
  for (b in 1:1000){
  Hcontrol[[a]][[b]]<- ALLdata[[a]][[b]][which(ALLdata[[a]][[b]]$allocation==0),]
  }
}

HexpTP <- list()
for (a in 1:8){
  HexpTP[[a]]<-list()
  for (b in 1:1000){
  HexpTP[[a]][[b]]<- ALLdata[[a]][[b]][which(ALLdata[[a]][[b]]$allocation==1),]
  }
}

HexpFP <- list()
for (a in 1:8){
  HexpFP[[a]]<-list()
  for (b in 1:1000){
  HexpFP[[a]][[b]]<- ALLdata[[a]][[b]][which(ALLdata[[a]][[b]]$allocation==2),]
  }
}
```

#Save datasets
```{r}
save(Hcontrol, file="1.DataSimulation_output/1.Hcontrol.Rdata")
save(HexpTP, file = "1.DataSimulation_output/1.HexpTP.Rdata")
save(HexpFP, file = "1.DataSimulation_output/1.HexpFP.Rdata")
```

## Extra: visualize & test assumptions

```{r}
load("0.DataPreperation_output/0.Historicaldata.RData") #Load Dcontrol
```

# Make a table that displays the estimated shape & scale parameters of the simulated and historical data
```{r}
#Obtain estimates for the historical and current controls
hist_survreg<- survreg(Surv(Dcontrol$STIME18, Dcontrol$STATUS18, type = "right") ~ 1, dist = "weibull")
curr_survreg<- survreg(Surv(Hcontrol[[1]][[1]]$survivalcensored, Hcontrol[[1]][[1]]$StatusIndicator, type = "right") ~ 1, dist = "weibull")

# Make a table that displays the estimated shape & scale parameters of the simulated and historical data
parameters <- round(matrix((c(1/hist_survreg$scale, exp(hist_survreg$coefficients), 1/curr_survreg$scale, exp(curr_survreg$coefficients))), ncol = 2, nrow = 2),2)

#Add rownames and colnames
colnames(parameters) <- c('hist', 'cur')
rownames(parameters) <- c('shape', 'scale')

#Display the table
parameters
```


#Function that tests assumption of proportional hazards
```{r}
assumptionHR <- function (df)
{
fit <- coxph(Surv(time=survivaltime, event=event)~indicator, data = data.frame(
survivaltime=c(Dcontrol$STIME18, df$survivalcensored),
event = c(Dcontrol$STATUS18, df$StatusIndicator),
indicator=c(rep(1, length(Dcontrol$STIME18)),rep(0, length(df$survivalcensored)))))
return(cox.zph(fit))
}
```

#Test assumption for Hcontrol[[1]][[1]]
```{r}
assumptionHR(Hcontrol[[1]][[1]])
```
The assumption is met; p > 0.05

#Function to make Hazard Rates plot
```{r}
HRplot <- function(df)
{
plot <- plot(survfit(Surv(time=survivaltime, event=event, type = "right")~indicator, data = data.frame(
survivaltime=c(Dcontrol$STIME18, df$survivalcensored),
event = c(Dcontrol$STATUS18, df$StatusIndicator),
indicator=c(rep(1, length(Dcontrol$STIME18)),rep(0, length(df$survivalcensored))))), main = "Plot of Survival Curves by treatment", xlab = "Length of Survival",ylab="Proportion of Individuals who have Survived",col=c("blue","red"), mark.time=TRUE) #mark.time are censoring markers
legend("topright", legend=c("Current", "Historical"),fill=c("blue","red"),bty="n")
return(plot)
}
```

#Use GGplot2 to make hazard plots
```{r}
library("ggplot2")
library("survival")
library("survminer")

#Compute two survival curves
Historical <- survfit( Surv(STIME18, STATUS18) ~ 1, data = Dcontrol)
Current <- survfit( Surv(survivalcensored, StatusIndicator) ~ 1, data = Hcontrol[[1]][[1]])

#Combine the two survival curves on one graph:
fit <- list(Historical = Historical, Current = Current)
ggsurvplot(fit, combine = TRUE, # Combine curves
           surv.median.line = "hv", # Add medians survival
           risk.table = TRUE,                  # Add risk table
           conf.int = TRUE,                    # Add confidence interval
           pval = TRUE,                        # Add p-value and tervals
           conf.int.style = "step",            # CI style, use "step" or "ribbon"
           censor = FALSE,                     # Remove censor points
           tables.theme = theme_cleantable(),  # Clean risk table
           legend.title = "Data",              # Change legends: title & labels
           legend.labs = c("Historical","Current"),
            # Color palettes. Use custom color: c("#E7B800", "#2E9FDF"),
            # or brewer color (e.g.: "Dark2"), or ggsci color (e.g.: "jco")
           palette = c("#E7B800", "#2E9FDF"),
           #ggtheme = theme_bw() # Change ggplot2 theme
           
           )                      
``` 

#Make function to give the average number of events (StatusIndicator = 1)
```{r}
sumlist <- function(list){

sum <- vector(length = 100)

for(i in 1:100){
 subset <- list[[i]]
 sum[i] <- sum(subset$StatusIndicator)
}
 mean_sum <- mean(sum)  
 return(mean_sum)
}
```

#Give the average number of events for every simulated dataset
```{r}
Nevents <- matrix(c(
sumlist(list = Data11_list),
sumlist(list = Data12_list),
sumlist(list = Data13_list),
sumlist(list = Data14_list),
sumlist(list = Data21_list),
sumlist(list = Data22_list),
sumlist(list = Data23_list),
sumlist(list = Data24_list)), ncol = 2, nrow = 4)

colnames(Nevents) <- c('scalepar = 429', 'scalepar = 403')
rownames(Nevents) <- c('sdrandomcluster = 0', 'sdrandomcluster = 0.1', 'sdrandomcluster = 0.2','sdrandomcluster = 0.4')

Nevents
```

