---
title: "2.5. RMST equivalence "
author: "Joukje Willemsen"
date: "13-05-2020"
output: html_document
---
In this document the confidence intervals of the RMST test are calculated for the scenarios referred to as A, B, C1-3 and D1-3 in the article.

Please note that:

Data11 = Scenario A

Data12 = Scenario C1

Data13 = Scenario C2

Data14 = Scenario C3

Data21 = Scenario B

Data22 = Scenario D1

Data23 = Scenario D2

Data24 = Scenario D3

#Load simulated & historical data
```{r}
load("1.DataSimulation_output/1.Hcontrol.Rdata")
load("0.DataPreperation_output/0.Historicaldata.RData")
```

#Load packages
```{r}
library(survival)
library(dplyr)
library(survival)
```

#Calculate the restricted mean survival time and SE for the historical control
```{r}
#Make a survfit object for the historical control data
survfit_hist <- survfit(Surv(time = STIME18, event = STATUS18, type = "right") ~ 1, data = Dcontrol)

#Abstract the estimated mean and SE form the survfit object
rmeanH <- (survival:::survmean(survfit_hist, rmean=548) [[1]]["*rmean"]) #RMST
seH <- (survival:::survmean(survfit_hist, rmean=548) [[1]]["*se(rmean)"]) #SE
```

#Function to calculate the CI
```{r}
get_rmeanCI <- function(dataC, alpha = 0.05){
  
  #Make a survfit object for the current control data
  survfitC <- survfit(Surv(time = survivalcensored, event = StatusIndicator, type = "right") ~ 1, data = dataC)
  
  #Abstract the estimated mean and SE form the survfit object
  rmeanC <- survival:::survmean(survfitC, rmean=548) [[1]]["*rmean"] #RMST
  seC <- survival:::survmean(survfitC, rmean=548) [[1]]["*se(rmean)"] #SE
 
  #Calculate estimated difference
  delta <- rmeanC - rmeanH
  
  #Calculate the estimated sampling variance combined
  SE <- sqrt(seC^2 + seH^2)
  
  LL <- delta - 1.96*SE #Lower Limit
  UL <- delta + 1.96*SE #Upper Limit
  
  CI <- c(LL, UL) #95%CI
  
  return (CI)
}
```

Example
```{r}
get_rmeanCI(Hcontrol[[1]][[1]])
```
The calculated CI of the RMST is [-42.66, 28,54]

#Function that returns a matrix with all the CI's using function get_rmeanCI
```{r}
RMSTmatrix <- function (list){ 
  
#Make a matrix to store the CIs
df <- matrix(ncol = 2, nrow = 1000) %>% data.frame()
for(i in 1:1000){
#Store the estimated CI in the matrix
df[i,] <- get_rmeanCI(list[[i]])
}
return(df) #Return the matrix
}
```

#Make a list with all the results
```{r}
#Apply RMSTmatrix to every simulated scenario
CIsRMEAN<-lapply(Hcontrol, FUN = RMSTmatrix)

#Name the lists
names(CIsRMEAN) <- c("Data11","Data12","Data13","Data14","Data21","Data22","Data23","Data24")
```

#Save CIs
```{r}
save(CIsRMEAN, file = "2.PoolingMethods_output/2.5.CIsRMEAN3.Rdata")
```













