---
title: "2.1 AlwaysPool"
author: "Joukje Willemsen"
date: "13-05-2020"
output: html_document
---

In  this docyment the "alwayspooled" controlgroups are created by combining the historical control group with the simulated control group for the scenarios referred to as A, B, C1-3 and D1-3 in the article.

Please note that:

Data11 = Scenario A

Data12 = Scenario C1

Data13 = Scenario C2

Data14 = Scenario C3

Data21 = Scenario B

Data22 = Scenario D1

Data23 = Scenario D2

Data24 = Scenario D3

#Load simulated & historical data
```{r}
load("1.DataSimulation_output/1.Hcontrol.Rdata")
load("0.DataPreperation_output/0.Historicaldata.RData")
```

#Make function that combines the current control group with the historical group
```{r}
pool <- function (dataset) 
{
#make a list called datasetpooled
datasetpooled <- list() 

for (i in 1:(length(dataset)))
  {
datasetpooled[[i]] <- data.frame(
  survivalcensored = c(dataset[[i]]$survivalcensored, Dcontrol$STIME18), #combine historical & current controls for variable "survivalcensored"
  StatusIndicator = c(dataset[[i]]$StatusIndicator, Dcontrol$STATUS18),  #combine historical & current controls for variable "StatusIndicator"
  pooled = "yes")
  }

return(datasetpooled)  
}
```

#Apply function to each simulated scenario
```{r}
AlwaysPoolData <- list("Data11" = pool(Hcontrol[[1]]), 
                      "Data12" = pool(Hcontrol[[2]]),
                      "Data13" = pool(Hcontrol[[3]]),
                      "Data14" = pool(Hcontrol[[4]]),
                      "Data21" = pool(Hcontrol[[5]]), 
                      "Data22" = pool(Hcontrol[[6]]),
                      "Data23" = pool(Hcontrol[[7]]),
                      "Data24" = pool(Hcontrol[[8]]))
```

#Save datasets
```{r}
save(AlwaysPoolData, file = "2.PoolingMethods_output/2.1.AlwaysPoolDataset.Rdata")
```

