---
title: "2.3 Obtaining CIs for the HR equivalence test"
author: "Joukje Willemsen"
date: "13-05-2020"
output: html_document
---

In this document the confidence intervals of the HR test are calculated for the scenarios referred to as A, B, C1-3 and D1-3 in the article.

Please note that:

Data11 = Scenario A

Data12 = Scenario C1

Data13 = Scenario C2

Data14 = Scenario C3

Data21 = Scenario B

Data22 = Scenario D1

Data23 = Scenario D2

Data24 = Scenario D3

#Load simulated & historical data
```{r}
load("1.DataSimulation_output/1.Hcontrol.Rdata")
load("0.DataPreperation_output/0.Historicaldata.RData")
```

#Load packages
```{r}
library(survival)
library(dplyr)
```

#Function that gives the CI of the HR
```{r}
eqHR <- function (df)
{
# Create dataset as input, where both the historical controls and the input dataset is included
fit <- coxph(Surv(time=survivaltime, event=event)~indicator, data = data.frame(
survivaltime=c(Dcontrol$STIME18, df$survivalcensored),
event = c(Dcontrol$STATUS18, df$StatusIndicator),
indicator=c(rep(1, length(Dcontrol$STIME18)),rep(0, length(df$survivalcensored)))))

# return the confidence interval
return(exp(confint(fit)) )
}
```

Test eqHR function
```{r}
eqHR(Hcontrol[[1]][[1]])
```
The confidence interval of the hazard rate ranges between 0.70 and 1.48


#Function that returns a matrix with all the CI's using function eqHR
```{r}
eqHRmatrix <- function (list){
#Make a matrix to store the CIs
df <- matrix(ncol = 2, nrow = 1000) %>% data.frame()
colnames(df) <- c("LowerCI", "UpperCI")
for(i in 1:1000){
#Store CIs for every simulated dataset
df[i,] <- eqHR(list[[i]])
}
return(df)
}
```

#Store the results
```{r}
#Apply the function to every simulated scenario
CIsHR <-lapply(Hcontrol, FUN = eqHRmatrix)

#Add names to the simulated scenarios
names(CIsHR) <- c("Data11","Data12","Data13","Data14","Data21","Data22","Data23","Data24")

#Save the matrices
save(CIsHR, file = "2.PoolingMethods_output/2.3.CIsHR.Rdata")
```


