---
title: "2.2.TestThenPool"
author: "Joukje Willemsen"
date: "13-05-2020"
output: html_document
---
In  this document the decision to pool or not is determined by a regular TTP test for the scenarios referred to as A, B, C1-3 and D1-3 in the article.

Please note that:

Data11 = Scenario A

Data12 = Scenario C1

Data13 = Scenario C2

Data14 = Scenario C3

Data21 = Scenario B

Data22 = Scenario D1

Data23 = Scenario D2

Data24 = Scenario D3

#Load simulated & historical data
```{r}
load("1.DataSimulation_output/1.Hcontrol.Rdata")
load("0.DataPreperation_output/0.Historicaldata.RData")
```

#Load packages
```{r}
library(survival)
library(dplyr)
```

#Obtain p-value from the HR difference test
```{r}
getpvalue <- function (df)
{
# Create dataset as input, where both the historical controls and the input dataset is included
dataset <- list(start=c(Dcontrol$STIME18, df$survivalcensored),
                stop =c(Dcontrol$STATUS18, df$StatusIndicator),
                event = c(rep(1, length(Dcontrol$STATUS18)), rep(0, length(df$StatusIndicator))))
#perform the HR difference test
result <- summary(coxph( Surv(start, stop) ~ event, dataset))
#the p-value obtained from the logtest is extracted
return(result$logtest[3])
}
```

test function
```{r}
getpvalue(Hcontrol[[1]][[1]])
```

#Function that returns vector with all the p-values of all the simulate datasets
```{r}
pvaluematrix <- function (list){
#Make a matrix to store the p-values
df <- matrix(ncol = 1, nrow = 1000) %>% data.frame()
for(i in 1:1000){
#Store p-values for every simulated dataset
df[i,] <- getpvalue(list[[i]]) #for every simulated dataset, obtain the pvalue and store in df
}
return(df)
}
```

#Make a list with all the results
```{r}
#Apply the function to every simulated scenario
pvaluematrices<-lapply(Hcontrol, FUN = pvaluematrix)

#Add names to the simulated scenarios
names(pvaluematrices) <- c("Data11","Data12","Data13","Data14","Data21","Data22","Data23","Data24")

#Save the matrices
save(pvaluematrices, file = "2.PoolingMethods_output/2.2.PvaluesTTP.Rdata")
```

