---
title: "3.FinalAnalysis RMST scenario A,B,C1-3 and D1-3"
author: "Joukje Willemsen"
date: "14-05-20"
output: html_document
---

In this document different decisionthresholds are applied for every poolingmethod, a RMST test is performed as final analysis to obtain the FPR and TPR for every poolingmethod and every decisionthreshold in every simulated scenario, referred to as A, B, C1-3 and D1-3 in the article.

Please note that:

Data11 = Scenario A

Data12 = Scenario C1

Data13 = Scenario C2

Data14 = Scenario C3

Data21 = Scenario B

Data22 = Scenario D1

Data23 = Scenario D2

Data24 = Scenario D3

#Load packages
```{r}
library(survival)
library(dplyr)
```

Recall that every simulated dataset is subjected to every pooling method. The outcome of the pooling method can be either "pool" or "not pool". 

First I want to create datasets with the outcome (a true positive or a false negative) for every simulated dataset 

#Load the datasets where nothing is pooled and everything is pooled
```{r}
#Never pool
load("1.DataSimulation_output/1.Hcontrol.Rdata")
NeverPool <- Hcontrol

#Always pool
load("2.PoolingMethods_output/2.1.AlwaysPoolDataset.Rdata")
AlwaysPool <- AlwaysPoolData
```

#Store them in a list
```{r}
Controlgroup <- list(NeverPool = NeverPool,
                     AlwaysPool = AlwaysPool)
```

#Load experimental data
```{r}
load("1.DataSimulation_output/1.HexpTP.Rdata")
load("1.DataSimulation_output/1.HexpFP.Rdata")
load("1.DataSimulation_output/1.Hcontrol.Rdata")
```

#Function that gives p value control vs exp
```{r}

get_decision_rmean <- function(dataC, dataE, alpha = 0.05){
  
  #Make a survfit object for both the experimental and control data
  survfitC <- survfit(Surv(time = survivalcensored, event = StatusIndicator, type = "right") ~ 1, data = dataC)
  
  survfitE <- survfit(Surv(time = survivalcensored, event = StatusIndicator, type = "right") ~ 1, data = dataE)
  
  #Abstract the estimated mean and SE form the survfit object
  
  rmeanC <- survival:::survmean(survfitC, rmean=548) [[1]]["*rmean"]
  seC <- survival:::survmean(survfitC, rmean=548) [[1]]["*se(rmean)"]
  
  rmeanE <- survival:::survmean(survfitE, rmean=548) [[1]]["*rmean"]
  seE <- survival:::survmean(survfitE, rmean=548) [[1]]["*se(rmean)"]
  
  #Calculate estimated difference
  delta <- rmeanE - rmeanC
  
  #Calculate the estimated sampling variance combined
  SE <- sqrt(seE^2 + seC^2)
  
  #To test the null hypothesis (true) delta = 0 is made by comparing deta_est/SE_est with a standard normal distribution
  
  statistic <- delta/SE
  
  pvalue <- dnorm(statistic)
  
  return(pvalue)
}
```

Make a function that gives Pvalues in a matrix
```{r}
#Pvalues[Alwayspool/Neverpool][situatie1t/m8][1tm1000][2colommen:FP&TP]
PvaluesMatrices <- function(HexpTP, HexpFP, cont){
  
  pvaluesmatrix <- matrix(NA, nrow = 1000, ncol = 2) 
  colnames(pvaluesmatrix) <- c("TP", "FP")

  for (i in 1:1000){#replication
    pvaluesmatrix[i,1] <- get_decision_rmean(dataC = cont[[i]], dataE = HexpTP[[i]])
    pvaluesmatrix[i,2] <- get_decision_rmean(dataC = cont[[i]], dataE = HexpFP[[i]])
    }
  result <- pvaluesmatrix
  return(result)
}
```

#Apply to every dataset, make two big lists: alwayspool(expTP & expFP) & neverpool(expTP & expFP) - takes some time!
```{r}
#or uncommend the next line:
#load("3.FinalAnalysis_output/3.PvaluesAlwaysNeverPoolrmean.Rdata")

PAlwaysPool <- list() #make a list

#For every simulated scenario (8 in total), execute the PvalueMatrices function in a situation where not one controlgroup is pooled and a situation where every controlgroup is pooled

for (i in 1:8){ 
  PAlwaysPool[[i]] <- PvaluesMatrices(HexpTP = HexpTP[[i]], HexpFP = HexpFP[[i]], cont = AlwaysPool[[i]])
}
names(PAlwaysPool) <- c("Data11","Data12","Data13","Data14","Data21","Data22","Data23","Data24")

PNeverPool <- list() #make a list

for (i in 1:8){
  PNeverPool[[i]] <- PvaluesMatrices(HexpTP = HexpTP[[i]], HexpFP = HexpFP[[i]], cont = NeverPool[[i]])
}
names(PNeverPool) <- c("Data11","Data12","Data13","Data14","Data21","Data22","Data23","Data24")

Pvalues <- list(PAlwaysPool=PAlwaysPool, PNeverPool=PNeverPool)

save(Pvalues, file = "3.FinalAnalysis_output/3.PvaluesAlwaysNeverPoolrmean.Rdata")
```


#Specify decsion for every dataset in both alwayspool & neverpool
```{r}
Decisions <- Pvalues #replicate the list of lists...
pcrit<- 0.05

for (a in 1:2){ #Alwayspool & Neverpool
  for (b in 1:8){ #situation
    for (c in 1:1000){ #replication

Decisions[[a]][[b]][[c,1]] <-
 if_else(Pvalues[[a]][[b]][c,1] <= pcrit, true = 1, false = 0, missing = NULL)      
Decisions[[a]][[b]][[c,2]] <-
 if_else(Pvalues[[a]][[b]][c,2] <= pcrit, true = 1, false = 0, missing = NULL)      
    }}}

#1 means significant effect
#0 means not significant effect

save(Decisions, file = "3.FinalAnalysis_output/3.DecisionsAlwaysNeverPoolrmean.Rdata")
```



Now we have for every simulated dataset what the decision would be when the dataset is pooled and what the decision would be when the dataset is not pooled for a situation where there's an effect (HR = 0.5) and a situation where there's no effect (HR = 1). 

Instead of pooling datasets together and calculating the p-values, we can now extract de final p-values/decisions if we know the decision (pool or not pool) of every method

###Different poolingmethods

```{r}
#Make function that indicates whether the outcome would be "pool" or "not pool" given a specified threshold, pcrit

testthenpool_decision <- function (pvalue, pcrit = 0.05){ #change eqregion
  if (pvalue >= pcrit){decision <- "pool"}
  else if (pvalue < pcrit){decision <- "notpool"}
  return(decision)
}
```

```{r}
#Prepare for storing data
PoolDecisions <- list() #Make a list to store the decision "pool" or "not pool"
PoolDecisions$TTP <- list() #Within this list make a list for the pooling method TTP
Decisions$PTTP <- list() 
```

#TTP - varier beslissingsdrempel & store results
```{r}
load("2.PoolingMethods_output/2.2.PvaluesTTP.Rdata")

#Make a vector with all the critical thresholds that will be evaluated
pcritvector <- c(0, 0.0001, 0.001, 0.01, 0.02, 0.03, 0.04, 0.05, 0.06, 0.07, 0.08, 0.09, 0.1, 0.15, 0.2, 0.25, 0.3, 0.35, 0.4, 0.45, 0.5, 0.55, 0.6, 0.65, 0.7, 0.75, 0.8, 0.85, 0.9, 0.95, 0.99, 0.999, 0.9999, 1)

#Make a list for every threshold
for (a in 1:length(pcritvector)){
  PoolDecisions$TTP[[a]] <- list() #make list for every different threshold
  Decisions$PTTP[[a]]<-list() #make list for every different threshold
  
#make a decision about whether to pool or not based on the threshold and store the decision
for (b in 1:8){
PoolDecisions$TTP[[a]][[b]] <- apply(pvaluematrices[[b]], MARGIN = 1, FUN = testthenpool_decision, pcrit = pcritvector[a]) 
  
Decisions$PTTP[[a]][[b]]<- matrix(NA, nrow = 1000, ncol = 2) #make a matrix to store the 

#Add colnames
colnames(Decisions$PTTP[[a]][[b]]) <- c("TP", "FP")
  
#Given whether the datasets are pooled or not, return the decision for the final analysis (significant or not)
for (c in 1:1000) {

#if the decision is pool, extract the decision based on the significance from "alwayspool", otherwise extract from "neverpool". Do this for both the situation where there's an effect (column 1) and where there's no effect (column 2)
  Decisions$PTTP[[a]][[b]][c,1] <- if_else(PoolDecisions$TTP[[a]][[b]][c]== "pool", true = Decisions$PAlwaysPool[[b]][c,1], false = Decisions$PNeverPool[[b]][c,1])
  
  Decisions$PTTP[[a]][[b]][c,2] <- if_else(PoolDecisions$TTP[[a]][[b]][c]== "pool", true = Decisions$PAlwaysPool[[b]][c,2], false = Decisions$PNeverPool[[b]][c,2])
}
}
}

sum(Decisions$PAlwaysPool[[7]][,1])
sum(PoolDecisions$TTP[[1]][[8]]=="pool")
sum(PoolDecisions$TTP[[length(pcritvector)]][[8]]=="pool")
```

#CIs - varier beslissingsdrempel & store results
CIs HR
```{r}
#Load the CIs
load("2.PoolingMethods_output/2.3.CIsHR.Rdata")

#Load function
topoolornot <- dget("functions/topoolornot.R")

#PoolDecisions <- list()
PoolDecisions$CIsHR <- list()
Decisions$PHR <- list()
eqregionmatrix = matrix(c(c(0.00001, 1/(0.00001)),
                          c(0.001, 1/(0.001)),
                          c(0.01, 1/(0.01)),
                          c(0.1, 1/(0.1)),
                          c(0.2, 1/(0.2)),
                          c(0.25, 1/(0.25)),
                          c(0.3, 1/(0.3)),
                          c(0.35, 1/(0.35)),
                          c(0.4, 1/(0.4)),
                          c(0.45, 1/(0.45)),
                          c(0.475, 1/(0.475)),
                          c(0.5, 1/(0.5)),
                          c(0.525, 1/(0.525)),
                          c(0.55, 1/(0.55)),
                          c(0.575, 1/(0.575)),
                          c(0.6, 1/(0.6)),
                          c(0.625, 1/(0.625)),
                          c(0.65, 1/(0.65)),
                          c(0.66, 1/(0.66)),
                          c(0.67, 1/(0.67)),
                          c(0.675, 1/(0.675)),
                          c(0.68, 1/(0.68)),
                          c(0.69, 1/(0.69)),
                          c(0.7, 1/(0.7)),
                          c(0.8, 1/(0.8)),
                          c(0.9, 1/(0.9)),
                          c(0.999, 1/(0.999))),
                        nrow=27,              # number of rows 
                        ncol=2,              # number of columns 
                        byrow = TRUE)        # fill matrix by rows 


#different thresholds
for (a in 1:nrow(eqregionmatrix)){
  PoolDecisions$CIsHR[[a]] <- list() #make list for every different threshold
  Decisions$PHR[[a]]<-list() #make list for every different threshold

#different situations
for (b in 1:8){
  PoolDecisions$CIsHR[[a]][[b]] <- apply(CIsHR[[b]], MARGIN = 1, FUN = topoolornot, eqregion = eqregionmatrix [a,]) #make a decision based on the threshold and store the decision
  
  Decisions$PHR[[a]][[b]]<- matrix(NA, nrow = 1000, ncol = 2) #make a matrix to store the TP & FP
  colnames(Decisions$PHR[[a]][[b]]) <- c("TP", "FP")
 
#different simulated datasets
for (c in 1:1000) {

#if the decision is pool, extract the decision based on the significance from "alwayspool", otherwise extract from "neverpool". Do this for both the situation where there's an effect (column 1) and where there's no effect (column 2)
  Decisions$PHR[[a]][[b]][c,1] <- if_else(PoolDecisions$CIsHR[[a]][[b]][c]== "pool", true = Decisions$PAlwaysPool[[b]][c,1], false = Decisions$PNeverPool[[b]][c,1])
  
  Decisions$PHR[[a]][[b]][c,2] <- if_else(PoolDecisions$CIsHR[[a]][[b]][c]== "pool", true = Decisions$PAlwaysPool[[b]][c,2], false = Decisions$PNeverPool[[b]][c,2])
}
}
}
```


CIs HR Boot
```{r}
#Load the bootstrapped CIs
load("2.PoolingMethods_output/2.4.BootCIsHR.Rdata")
#load("2.PoolingMethods_output/2.4.BootCIsHR700.Rdata")

#Load function
topoolornot <- dget("functions/topoolornot.R")

#PoolDecisions <- list()
PoolDecisions$BootCIsHR <- list()
Decisions$PHRboot <- list()

eqregionmatrix = matrix(c(c(0.00001, 1/(0.00001)),
                          c(0.001, 1/(0.001)),
                          c(0.01, 1/(0.01)),
                          c(0.1, 1/(0.1)),
                          c(0.2, 1/(0.2)),
                          c(0.25, 1/(0.25)),
                          c(0.3, 1/(0.3)),
                          c(0.35, 1/(0.35)),
                          c(0.4, 1/(0.4)),
                          c(0.45, 1/(0.45)),
                          c(0.475, 1/(0.475)),
                          c(0.5, 1/(0.5)),
                          c(0.525, 1/(0.525)),
                          c(0.55, 1/(0.55)),
                          c(0.575, 1/(0.575)),
                          c(0.6, 1/(0.6)),
                          c(0.625, 1/(0.625)),
                          c(0.65, 1/(0.65)),
                          c(0.66, 1/(0.66)),
                          c(0.67, 1/(0.67)),
                          c(0.675, 1/(0.675)),
                          c(0.68, 1/(0.68)),
                          c(0.69, 1/(0.69)),
                          c(0.7, 1/(0.7)),
                          c(0.8, 1/(0.8)),
                          c(0.9, 1/(0.9)),
                          c(0.999, 1/(0.999))),
                        nrow=27,              # number of rows 
                        ncol=2,              # number of columns 
                        byrow = TRUE)        # fill matrix by rows 

#different thresholds
for (a in 1:nrow(eqregionmatrix)){
  PoolDecisions$BootCIsHR[[a]] <- list() #make list for every different threshold
  Decisions$PHRboot[[a]]<-list() #make list for every different threshold

#different situations
for (b in 1:8){
  PoolDecisions$BootCIsHR[[a]][[b]] <- apply(BootCIsHR[[b]], MARGIN = 1, FUN = topoolornot, eqregion = eqregionmatrix [a,]) #make a decision based on the threshold and store the decision
  
  Decisions$PHRboot[[a]][[b]]<- matrix(NA, nrow = 1000, ncol = 2) #make a matrix to store the TP & FP
  colnames(Decisions$PHRboot[[a]][[b]]) <- c("TP", "FP")
 
#different simulated datasets
for (c in 1:1000) {

#if the decision is pool, extract the decision based on the significance from "alwayspool", otherwise extract from "neverpool". Do this for both the situation where there's an effect (column 1) and where there's no effect (column 2)
  Decisions$PHRboot[[a]][[b]][c,1] <- if_else(PoolDecisions$BootCIsHR[[a]][[b]][c]== "pool", true = Decisions$PAlwaysPool[[b]][c,1], false = Decisions$PNeverPool[[b]][c,1])
  
  Decisions$PHRboot[[a]][[b]][c,2] <- if_else(PoolDecisions$BootCIsHR[[a]][[b]][c]== "pool", true = Decisions$PAlwaysPool[[b]][c,2], false = Decisions$PNeverPool[[b]][c,2])
}
}
}

```

# CI's Rmean 
```{r}
load("2.PoolingMethods_output/2.5.CIsRMEAN3.Rdata")
load("0.DataPreperation_output/0.Historicaldata.Rdata")

#get difference
survfit_hist <- survfit(Surv(time = STIME18, event = STATUS18, type = "right") ~ 1, data = Dcontrol)
rmean_hist <- (survival:::survmean(survfit_hist, rmean=548) [[1]]["*rmean"])

CIsRMEANdiff <- CIsRMEAN

#Load function
topoolornot <- dget("functions/topoolornot.R")

#PoolDecisions <- list()
PoolDecisions$CIsRMEANdiff <- list()
Decisions$PRMEANdiff <- list()

eqregionmatrix = matrix(c(c(-0, 0),
                          c(-10, 10),
                          c(-20, 20),
                          c(-30, 30),
                          c(-35, 35),
                          c(-37.5, 37.5),
                          c(-40, 40),
                          c(-42.5, 42.5),
                          c(-45, 45),
                          c(-47.5, 47.5),
                          c(-50, 50),
                          c(-52.5, 52.5),
                          c(-55, 55),
                          c(-57.5, 57.5),
                          c(-60, 60),
                          c(-62.5, 62.5),
                          c(-65, 65),
                          c(-67.5, 67.5),
                          c(-70, 70),
                          c(-75, 75),
                          c(-80, 80),
                          c(-85, 85),
                          c(-90, 90),
                          c(-95, 95),
                          c(-100, 100),
                          c(-110, 110),
                          c(-150, 150),
                          c(-1000, 1000)),
                        nrow=28,              # number of rows 
                        ncol=2,              # number of columns 
                        byrow = TRUE)        # fill matrix by rows 

#different thresholds
for (a in 1:nrow(eqregionmatrix)){
  PoolDecisions$CIsRMEANdiff[[a]] <- list() #make list for every different threshold
  Decisions$PRMEANdiff[[a]]<-list() #make list for every different threshold

  for (b in 1:length(CIsRMEANdiff)){
  PoolDecisions$CIsRMEANdiff[[a]][[b]] <- apply(CIsRMEANdiff[[b]], MARGIN = 1, FUN = topoolornot, eqregion = eqregionmatrix [a,]) #make a decision based on the threshold and store the decision
 
  Decisions$PRMEANdiff[[a]][[b]]<- matrix(NA, nrow = 1000, ncol = 2) #make a matrix to store the TP & FP
  colnames(Decisions$PRMEANdiff[[a]][[b]]) <- c("TP", "FP")
  
  #different situations
  
#different simulated datasets
for (c in 1:1000) {

#if the decision is pool, extract the decision based on the significance from "alwayspool", otherwise extract from "neverpool". Do this for both the situation where there's an effect (column 1) and where there's no effect (column 2)
  Decisions$PRMEANdiff[[a]][[b]][c,1] <- if_else(PoolDecisions$CIsRMEANdiff[[a]][[b]][c]== "pool", true = Decisions$PAlwaysPool[[b]][c,1], false = Decisions$PNeverPool[[b]][c,1])
  Decisions$PRMEANdiff[[a]][[b]][c,2] <- if_else(PoolDecisions$CIsRMEANdiff[[a]][[b]][c]== "pool", true = Decisions$PAlwaysPool[[b]][c,2], false = Decisions$PNeverPool[[b]][c,2])
}
}
}

#topoolornot(CIsRMEANdiff[[1]][[1]], eqregion = eqregionmatrix[1,])
```


```{r}
load("2.PoolingMethods_output/2.6.Boot_CIsRMEANSNEL.Rdata")

#get difference
survfit_hist <- survfit(Surv(time = STIME18, event = STATUS18, type = "right") ~ 1, data = Dcontrol)
rmean_hist <- (survival:::survmean(survfit_hist, rmean=548) [[1]]["*rmean"])

BootCIsRMEANdiff <- list()
for (i in 1:8){
BootCIsRMEANdiff[[i]] <- BootCIsRMEAN[[i]]
}

#Load function
topoolornot <- dget("functions/topoolornot.R")

#PoolDecisions <- list()
PoolDecisions$BootCIsRMEANdiff <- list()
Decisions$PRMEANbootdiff <- list()

eqregionmatrix = matrix(c(c(0, 0),
                          c(-10, 10),
                          c(-20, 20),
                          c(-30, 30),
                          c(-35, 35),
                          c(-37.5, 37.5),
                          c(-40, 40),
                          c(-42.5, 42.5),
                          c(-45, 45),
                          c(-47.5, 47.5),
                          c(-50, 50),
                          c(-52.5, 52.5),
                          c(-55, 55),
                          c(-57.5, 57.5),
                          c(-60, 60),
                          c(-62.5, 62.5),
                          c(-65, 65),
                          c(-67.5, 67.5),
                          c(-70, 70),
                          c(-75, 75),
                          c(-80, 80),
                          c(-85, 85),
                          c(-90, 90),
                          c(-95, 95),
                          c(-100, 100),
                          c(-110, 110),
                          c(-150, 150),
                          c(-1000, 1000)),
                        nrow=28,              # number of rows 
                        ncol=2,              # number of columns 
                        byrow = TRUE)        # fill matrix by rows  

#different thresholds
for (a in 1:nrow(eqregionmatrix)){
  PoolDecisions$BootCIsRMEANdiff[[a]] <- list() #make list for every different threshold
  Decisions$PRMEANbootdiff[[a]]<-list() #make list for every different threshold

#different situations
for (b in 1:8){
  PoolDecisions$BootCIsRMEANdiff[[a]][[b]] <- apply(BootCIsRMEANdiff[[b]], MARGIN = 1, FUN = topoolornot, eqregion = eqregionmatrix [a,]) #make a decision based on the threshold and store the decision

  Decisions$PRMEANbootdiff[[a]][[b]]<- matrix(NA, nrow = 1000, ncol = 2) #make a matrix to store the TP & FP
  colnames(Decisions$PRMEANbootdiff[[a]][[b]]) <- c("TP", "FP")
  
#different simulated datasets
for (c in 1:1000) {

#if the decision is pool, extract the decision based on the significance from "alwayspool", otherwise extract from "neverpool". Do this for both the situation where there's an effect (column 1) and where there's no effect (column 2)
  Decisions$PRMEANbootdiff[[a]][[b]][c,1] <- if_else(PoolDecisions$BootCIsRMEANdiff[[a]][[b]][c]== "pool", true = Decisions$PAlwaysPool[[b]][c,1], false = Decisions$PNeverPool[[b]][c,1])
  
  Decisions$PRMEANbootdiff[[a]][[b]][c,2] <- if_else(PoolDecisions$BootCIsRMEANdiff[[a]][[b]][c]== "pool", true = Decisions$PAlwaysPool[[b]][c,2], false = Decisions$PNeverPool[[b]][c,2])
}
}
}
```

```{r}
save(Decisions, file="3.FinalAnalysis_output/3.DecisionsFinalAnalyses400rmean3.Rdata")
save(PoolDecisions, file = "3.FinalAnalysis_output/3.Pooldecisions400rmean3.Rdata")

#save(Decisions, file="3.FinalAnalysis_output/3.DecisionsFinalAnalyses700rmean3.Rdata")
#save(PoolDecisions, file = "3.FinalAnalysis_output/3.Pooldecisions700rmean3.Rdata")
```

Make a function that returns a list with matrices with proportions

```{r}
giveproportions <- function(poolingmethod){  
#input: poolingmethod = decisions$poolingmethod
  proportions <- list()
  for (i in 1:length(poolingmethod)){
    proportions[[i]] <- matrix(NA, nrow = 8, ncol = 5)
    rownames(proportions[[i]])<- c("Data11","Data12","Data13","Data14","Data21","Data22","Data23","Data24")
    colnames(proportions[[i]])<- c("TP", "FP", "TP_prop", "FP_prop", "TP/FP")
    for(a in 1:8){
      proportions[[i]][a,1] <- sum(poolingmethod[[i]][[a]][,1][1:1000])
      proportions[[i]][a,2] <- sum(poolingmethod[[i]][[a]][,2][1:1000])
      proportions[[i]][a,3] <- sum(poolingmethod[[i]][[a]][,1][1:1000]/1000)
      proportions[[i]][a,4] <- sum(poolingmethod[[i]][[a]][,2][1:1000]/1000)
      proportions[[i]][a,5] <-  proportions[[i]][a,3]/proportions[[i]][a,4]
    }}
  
  return(proportions)
}
```

```{r}
giveproportionsNOpool <- function(poolingmethod){
  #input: poolingmethod = decisions$poolingmethod
  proportions <- list()
  for (i in 1:length(poolingmethod)){
    proportions <- matrix(NA, nrow = 8, ncol = 5)
    rownames(proportions)<- c("Data11","Data12","Data13","Data14","Data21","Data22","Data23","Data24")
    colnames(proportions)<- c("TP", "FP", "TP_prop", "FP_prop", "TP/FP")
    for(a in 1:8){
      proportions[a,1] <- sum(poolingmethod[[a]][,1][1:1000])
      proportions[a,2] <- sum(poolingmethod[[a]][,2][1:1000])
      proportions[a,3] <- sum(poolingmethod[[a]][,1][1:1000]/1000)
      proportions[a,4] <- sum(poolingmethod[[a]][,2][1:1000]/1000)
      proportions[a,5] <-  proportions[a,3]/proportions[a,4]
    }}
  
  return(proportions)
}
```


Apply function
```{r}
proportions<-list()
 
#Apply first function
proportions$PPTTP<- giveproportions(Decisions$PTTP)
proportions$PRMEANbootdiff <- giveproportions(Decisions$PRMEANbootdiff)
proportions$RMEANdiff <-giveproportions(Decisions$PRMEANdiff)
proportions$PHRboot <- giveproportions(Decisions$PHRboot)
proportions$PHR <- giveproportions(Decisions$PHR)

#Apply second function
proportions$PNeverPool <- giveproportionsNOpool(Decisions$PNeverPool) #incorrect number of dimmensions
proportions$PAlwaysPool <- giveproportionsNOpool(Decisions$PAlwaysPool) #incorrect number of dimmensions

save(proportions, file="3.FinalAnalysis_output/3.ProportionsTPFPrmean3.Rdata")

```

