---
title: "Data visualization plots scenario A-D"
author: "Joukje Willemsen"
date: "14-05-2020"
output: html_document
---

In this document the TPR/FPR plots are created for every poolingmethod and every decisionthreshold in every simulated scenario, referred to as A, B, C1-3 and D1-3 in the article.

Please note that:

Data11 = Scenario A

Data12 = Scenario C1

Data13 = Scenario C2

Data14 = Scenario C3

Data21 = Scenario B

Data22 = Scenario D1

Data23 = Scenario D2

Data24 = Scenario D3

#Load packages
```{r}
library(dplyr) 
library(survival) 
library(ggplot2)
library(cowplot)
```

#Make a function that calculates how many datasets are pooled
```{r}
npool <- function(dataset, dat=1){
propvector<-vector()#Make a vector to store the proportions
for (i in 1:length(dataset)){
  propvector[i]<-sum(dataset[[i]][[dat]]=="pool")#store the proportion in propvector
}
return(propvector/1000)
}
```

#Make a function that returns a vector with the TPs, and a vector with the FPs for the indicated dataset
```{r}
makeDF <- function(proportions, dat=1){
TP <- vector() #a vector to store the true positive rate
FP <- vector() #a vector to store the false positive rate
for (i in 1:length(proportions)){
TP[i] = proportions[[i]][dat,3] #substract the TP from the proportions dataset
FP[i] = proportions[[i]][dat,4] #substract the FP from the proportions dataset
}
data <- data.frame(TP = TP, FP=FP)
return(data)
}
#plot(TP, FP)
```

#######################################
####### HR as final analysis###########
#######################################

#Load output from 3.FinalAnalysis
```{r}
load("3.FinalAnalysis_output/3.ProportionsTPFPHR.Rdata")
load("3.FinalAnalysis_output/3.DecisionsFinalAnalysesHR.Rdata")
load("3.FinalAnalysis_output/3.Pooldecisions400HR.Rdata") 
```

#Make a function to return FPR/TPR plot
```{r}
#specify the colours
cbPalette <- c("#999999", "#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#D55E00", "#CC79A7")

makeROCplot <- function(dat = 1, setxaxis, FPalwayspool, FPneverpool, TPalwayspool, TPneverpool)
{

#organize the input data for the different poolingmethods
data <- list()
data$TTP <- makeDF(proportions$PPTTP, dat = dat)
data$PRmeanbootdiff <- makeDF(proportions$PRMEANbootdiff, dat = dat)
data$PRMEANdiff <- makeDF(proportions$RMEANdiff, dat = dat)
data$PHRboot <- makeDF(proportions$PHRboot, dat = dat)
data$PHR <- makeDF(proportions$PHR, dat = dat)

#organize the input data for "alwayspool" and "neverpool"
points <- data.frame(
  "method" =  c("AlwaysPool", "NeverPool"),
  "FP" = c(FPalwayspool, FPneverpool),
  "TP" = c(TPalwayspool, TPneverpool))
  
#Make the plot
plot <- ggplot(data$PHR, aes(x=FP, y=TP))+
  
  #add lines
  geom_path(data= data$TTP, aes(x=FP, y=TP, colour = "HRdiff"), size = 1, show.legend = TRUE)+
  geom_path(data= data$PRmeanbootdiff, aes(x=FP, y=TP, colour = "RMSTboot"), size = 1, show.legend = TRUE)+
  geom_path(data= data$PRMEANdiff, aes(x=FP, y=TP, colour = "RMST"), size = 1)+
  geom_path(data= data$PHRboot, aes(x=FP, y=TP, colour = "HRboot"), size = 1)+
  geom_path(data= data$PHR, aes(x=FP, y=TP, colour = "HReq"), size = 1)+

  #add datapoints
  geom_point(data= data$TTP, aes(x=FP, y=TP, colour = "HRdiff"), size = 3)+
  geom_point(data= data$PRmeanbootdiff, aes(x=FP, y=TP, colour = "RMSTboot"), size = 3)+
  geom_point(data= data$PRMEANdiff, aes(x=FP, y=TP, colour = "RMST"), size = 3)+
  geom_point(data= data$PHRboot, aes(x=FP, y=TP, colour = "HRboot"), size = 3)+
  geom_point(data= data$PHR, aes(x=FP, y=TP, colour = "HReq"), size = 3)+
  
  #add datapoints always & never pool
  geom_point(data= points[1,], aes(x=FP, y=TP, shape = "Alwayspool"), colour = "black", size = 4)+
  geom_point(data= points[2,], aes(x=FP, y=TP, shape = "Neverpool"), colour = "black", size = 4)+
  
  #legend
  scale_shape_manual("", breaks = c("Alwayspool" = "Alwayspool", "Neverpool" = "Neverpool"), values = c(16,17)) +
  guides(linetype=FALSE) +
  guides(shape = guide_legend(override.aes = list(linetype = 0)))+
  scale_color_manual("", breaks = c("HRdiff" = "HRdiff", "RMSTboot"= "RMSTboot", "RMST" = "RMST", "HRboot" ="HRboot", "HReq" = "HReq"), values=cbPalette)+
  labs(colour="",linetype="",shape="")+
  
  #set x-axis
  coord_cartesian(xlim = setxaxis) + 

theme_cowplot(12)

return(plot)
}

```


#Make 1 big plot
```{r}
D11 <- makeROCplot(dat = 1, setxaxis = c(0.04,0.065), FPalwayspool = proportions$PAlwaysPool[1,4], FPneverpool = proportions$PNeverPool[1,4], TPalwayspool = proportions$PAlwaysPool[1,3], TPneverpool = proportions$PNeverPool[1,3])

D12 <- makeROCplot(dat = 2, setxaxis = c(0.04,0.1), FPalwayspool = proportions$PAlwaysPool[2,4], FPneverpool = proportions$PNeverPool[2,4], TPalwayspool = proportions$PAlwaysPool[2,3], TPneverpool = proportions$PNeverPool[2,3])

            
D13 <- makeROCplot(dat = 3, setxaxis = c(0.04,0.18), FPalwayspool = proportions$PAlwaysPool[3,4], FPneverpool = proportions$PNeverPool[3,4], TPalwayspool = proportions$PAlwaysPool[3,3], TPneverpool = proportions$PNeverPool[3,3]) #3,1

D14 <- makeROCplot(dat = 4, setxaxis = c(0.04,0.4), FPalwayspool = proportions$PAlwaysPool[4,4], FPneverpool = proportions$PNeverPool[4,4], TPalwayspool = proportions$PAlwaysPool[4,3], TPneverpool = proportions$PNeverPool[4,3]) #4,1

D21 <-  makeROCplot(dat = 5, setxaxis = c(0.04,0.19), FPalwayspool = proportions$PAlwaysPool[5,4], FPneverpool = proportions$PNeverPool[5,4], TPalwayspool = proportions$PAlwaysPool[5,3], TPneverpool = proportions$PNeverPool[5,3]) #1,2

D22 <- makeROCplot(dat = 6, setxaxis = c(0.04,0.23), FPalwayspool = proportions$PAlwaysPool[6,4], FPneverpool = proportions$PNeverPool[6,4], TPalwayspool = proportions$PAlwaysPool[6,3], TPneverpool = proportions$PNeverPool[6,3]) #2,2

D23 <- makeROCplot(dat = 7, setxaxis = c(0.04,0.3), FPalwayspool = proportions$PAlwaysPool[7,4], FPneverpool = proportions$PNeverPool[7,4], TPalwayspool = proportions$PAlwaysPool[7,3], TPneverpool = proportions$PNeverPool[7,3]) #3,2

D24 <- makeROCplot(dat = 8, setxaxis = c(0.04,0.45), FPalwayspool = proportions$PAlwaysPool[8,4], FPneverpool = proportions$PNeverPool[8,4], TPalwayspool = proportions$PAlwaysPool[8,3], TPneverpool = proportions$PNeverPool[8,3]) #4,2

#arrange the plots in one big plot
arrangedfigure <- ggpubr::ggarrange(D11, D21, D12, D22, D13, D23, D14, D24, 
         labels = c(" A ", " B ","C1", "D1", "C2", "D2", "C3", "D3"), #add lables
          ncol = 2, nrow = 4, common.legend = TRUE, vjust = +0.2, hjust = -1.6, align = "hv", legend = "bottom")

# add the text around the plots
annotatedfigureHR <- ggpubr::annotate_figure(arrangedfigure, 
               top = ggpubr::text_grob(expression(paste(lambda["c"],"= 776.89                                   ",lambda["c"],"= 876.89")), face = "bold", size = 20), 
              left = ggpubr::text_grob(expression(paste(sigma["s"],"=0.4                ", sigma["s"], "=0.2                ", sigma["s"], "=0.1                ", sigma["s"], "=0")), face = "bold", size = 20, rot = 90))

#show the plot
annotatedfigureHR

```

#######################################
############# RMST ####################
#######################################

#Load output from 3.FinalAnalysis
```{r}
load("3.FinalAnalysis_output/3.ProportionsTPFPrmean3.Rdata") 
load("3.FinalAnalysis_output/3.Pooldecisions400rmean3.Rdata") 
load("3.FinalAnalysis_output/3.DecisionsFinalAnalyses400rmean3.Rdata")
```

#Make a function to return FP/TP plot
```{r}
#color pallette
cbPalette <- c("#999999", "#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#D55E00", "#CC79A7")

#start function
makeROCplot <- function(dat = 1, setxaxis, FPalwayspool, FPneverpool, TPalwayspool, TPneverpool)
{
  
#organize input data for poolingmethods
data <- list()
data$TTP <- makeDF(proportions$PPTTP, dat = dat)
data$PRmeanbootdiff <- makeDF(proportions$PRMEANbootdiff, dat = dat)
data$PRMEANdiff <- makeDF(proportions$RMEANdiff, dat = dat)
data$PHRboot <- makeDF(proportions$PHRboot, dat = dat)
data$PHR <- makeDF(proportions$PHR, dat = dat)

#organize input data for "always pool" and "never pool"
points <- data.frame(
  "method" =  c("AlwaysPool", "NeverPool"),
  "FP" = c(FPalwayspool, FPneverpool),
  "TP" = c(TPalwayspool, TPneverpool))
  
#make plot
plot <- ggplot(data$PHR, aes(x=FP, y=TP))+
  
  #add lines poolingmethods
  geom_path(data= data$TTP, aes(x=FP, y=TP, colour = "HRdiff"), size = 1, show.legend = FALSE)+
  geom_path(data= data$PRmeanbootdiff, aes(x=FP, y=TP, colour = "RMSTboot"), size = 1, show.legend = FALSE)+
  geom_path(data= data$PRMEANdiff, aes(x=FP, y=TP, colour = "RMST"), size = 1, show.legend = FALSE)+
  geom_path(data= data$PHRboot, aes(x=FP, y=TP, colour = "HRboot"), size = 1, show.legend = FALSE)+
  geom_path(data= data$PHR, aes(x=FP, y=TP, colour = "HReq"), size = 1, show.legend = FALSE)+

  #add datapoints poolingmethods
  geom_point(data= data$TTP, aes(x=FP, y=TP, colour = "HRdiff"), size = 3, show.legend = FALSE)+
  geom_point(data= data$PRmeanbootdiff, aes(x=FP, y=TP, colour = "RMSTboot"), size = 3, show.legend = FALSE)+
  geom_point(data= data$PRMEANdiff, aes(x=FP, y=TP, colour = "RMST"), size = 3, show.legend = FALSE)+
  geom_point(data= data$PHRboot, aes(x=FP, y=TP, colour = "HRboot"), size = 3, show.legend = FALSE)+
  geom_point(data= data$PHR, aes(x=FP, y=TP, colour = "HReq"), size = 3, show.legend = FALSE)+
  
  #add datapoints "alwayspool" and "neverpool"
  geom_point(data= points[1,], aes(x=FP, y=TP, shape = "Alwayspool"), colour = "black", size = 4, show.legend = FALSE)+
  geom_point(data= points[2,], aes(x=FP, y=TP, shape = "Neverpool"), colour = "black", size = 4, show.legend = FALSE)+
  
  #legend
  scale_shape_manual("", breaks = c("Alwayspool" = "Alwayspool", "Neverpool" = "Neverpool"), values = c(16,17)) +
  guides(linetype=FALSE) +
  guides(shape = guide_legend(override.aes = list(linetype = 0)))+
  scale_color_manual("", breaks = c("HRdiff" = "HRdiff", "RMSTboot"= "RMSTboot", "RMST" = "RMST", "HRboot" ="HRboot", "HReq" = "HReq"), values=cbPalette)+
  labs(colour="",linetype="",shape="")+

  #set x-axis
  coord_cartesian(xlim = setxaxis) + 

theme_cowplot(12) #theme

return(plot)
}

```


#Make 1 big plot
```{r}
#Make a plot for every simulated scenario

D11 <- makeROCplot(dat = 1, setxaxis = c(0.045,0.07), FPalwayspool = proportions$PAlwaysPool[1,4], FPneverpool = proportions$PNeverPool[1,4], TPalwayspool = proportions$PAlwaysPool[1,3], TPneverpool = proportions$PNeverPool[1,3])

D12 <- makeROCplot(dat = 2, setxaxis = c(0.04,0.083), FPalwayspool = proportions$PAlwaysPool[2,4], FPneverpool = proportions$PNeverPool[2,4], TPalwayspool = proportions$PAlwaysPool[2,3], TPneverpool = proportions$PNeverPool[2,3])

            
D13 <- makeROCplot(dat = 3, setxaxis = c(0.04,0.14), FPalwayspool = proportions$PAlwaysPool[3,4], FPneverpool = proportions$PNeverPool[3,4], TPalwayspool = proportions$PAlwaysPool[3,3], TPneverpool = proportions$PNeverPool[3,3]) #3,1

D14 <- makeROCplot(dat = 4, setxaxis = c(0.04,0.32), FPalwayspool = proportions$PAlwaysPool[4,4], FPneverpool = proportions$PNeverPool[4,4], TPalwayspool = proportions$PAlwaysPool[4,3], TPneverpool = proportions$PNeverPool[4,3]) #4,1

D21 <-makeROCplot(dat = 5, setxaxis = c(0.04,0.18), FPalwayspool = proportions$PAlwaysPool[5,4], FPneverpool = proportions$PNeverPool[5,4], TPalwayspool = proportions$PAlwaysPool[5,3], TPneverpool = proportions$PNeverPool[5,3]) #1,2

D22 <- makeROCplot(dat = 6, setxaxis = c(0.04,0.2), FPalwayspool = proportions$PAlwaysPool[6,4], FPneverpool = proportions$PNeverPool[6,4], TPalwayspool = proportions$PAlwaysPool[6,3], TPneverpool = proportions$PNeverPool[6,3]) #2,2

D23 <- makeROCplot(dat = 7, setxaxis = c(0.04,0.25), FPalwayspool = proportions$PAlwaysPool[7,4], FPneverpool = proportions$PNeverPool[7,4], TPalwayspool = proportions$PAlwaysPool[7,3], TPneverpool = proportions$PNeverPool[7,3]) #3,2

D24 <- makeROCplot(dat = 8, setxaxis = c(0.04,0.4), FPalwayspool = proportions$PAlwaysPool[8,4], FPneverpool = proportions$PNeverPool[8,4], TPalwayspool = proportions$PAlwaysPool[8,3], TPneverpool = proportions$PNeverPool[8,3]) #4,2

#arrange the plots in one big figure
arrangedfigure <- ggpubr::ggarrange(D11, D21, D12, D22, D13, D23, D14, D24, 
          labels = c(" A ", " B ","C1", "D1", "C2", "D2", "C3", "D3"), #add labels
          ncol = 2, nrow = 4, common.legend = TRUE, vjust = +0.2, hjust = -1.6, align = "hv", legend = "bottom")

# add text in the figure
annotatedfigureRMST <- ggpubr::annotate_figure(arrangedfigure, 
               top = ggpubr::text_grob(expression(paste(lambda["c"],"= 776.89                                   ",lambda["c"],"= 876.89")), face = "bold", size = 20))

#show the plot
annotatedfigureRMST
```

#######################################
## Combine the HR plot and RMST plot ##
#######################################


Save plot in 4.DataVisualization_output
```{r}
arrangedfigureBOTH <- ggpubr::ggarrange(annotatedfigureHR, annotatedfigureRMST, 
          ncol = 2, nrow = 1, common.legend = TRUE, align = "hv", legend = "right")

annotatedfigureBOTH <- ggpubr::annotate_figure(arrangedfigureBOTH, 
               top = ggpubr::text_grob("HR as final analysis                                                                                  RMST as final analysis", face = "bold", size = 20))

#show the plot
annotatedfigureBOTH

#saveplot
ggsave("4.DataVisualization_output/1.Sim1.png", plot = annotatedfigureBOTH, width = 20, height = 10)
```

