---
title: "Untitled"
author: "Joukje Willemsen"
date: "4 mei 2020"
output: html_document
---

#Load packages
```{r}
library(dplyr) 
library(survival) 
library(ggplot2)
library(cowplot)
```

```{r}
npool <- function(dataset, dat=1){
  #PoolDecisions$TTP = PoolDecisions$TTP
propvector<-vector()
for (i in 1:length(dataset)){
  propvector[i]<-sum(dataset[[i]][[dat]]=="pool")
}
return(propvector/1000)
}
```

#Make a function that returns a vector with the TPs, and a vector with the FPs for the indicated dataset
```{r}
makeDF <- function(proportions, dat=1){ #example: proportions$PHR
TP <- vector()
FP <- vector()
for (i in 1:length(proportions)){
TP[i] = proportions[[i]][dat,3]
FP[i] = proportions[[i]][dat,4]
}
data <- data.frame(TP = TP, FP=FP)
return(data)
}
#plot(TP, FP)
```

#######################################
############# HR ######################
#######################################

#Load output from 3.FinalAnalysis
```{r}
load("3.FinalAnalysis_output/3.ProportionsTPFPHR.Rdata")
load("3.FinalAnalysis_output/3.DecisionsFinalAnalysesHR.Rdata")
#load("3.FinalAnalysis_output/3.Pooldecisions700HR.Rdata") 
load("3.FinalAnalysis_output/3.Pooldecisions400HR.Rdata") 
```

#Make a function to return FP/TP plot
```{r}
cbPalette <- c("#999999", "#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#D55E00", "#CC79A7")

makeROCplot <- function(dat = 1, setxaxis, FPalwayspool, FPneverpool, TPalwayspool, TPneverpool)
{
data <- list()
#data$TP <- rowbind()


data$TTP <- makeDF(proportions$PPTTP, dat = dat)
data$PRmeanbootdiff <- makeDF(proportions$PRMEANbootdiff, dat = dat)
data$PRMEANdiff <- makeDF(proportions$RMEANdiff, dat = dat)
data$PHRboot <- makeDF(proportions$PHRboot, dat = dat)
data$PHR <- makeDF(proportions$PHR, dat = dat)

points <- data.frame(
  "method" =  c("AlwaysPool", "NeverPool"),
  "FP" = c(FPalwayspool, FPneverpool),
  "TP" = c(TPalwayspool, TPneverpool))
  
plot <- ggplot(data$PHR, aes(x=FP, y=TP))+
  
  geom_path(data= data$TTP, aes(x=FP, y=TP, colour = "HRdiff"), size = 1, show.legend = TRUE)+
  geom_path(data= data$PRmeanbootdiff, aes(x=FP, y=TP, colour = "RMSTboot"), size = 1, show.legend = TRUE)+
  geom_path(data= data$PRMEANdiff, aes(x=FP, y=TP, colour = "RMST"), size = 1)+
  geom_path(data= data$PHRboot, aes(x=FP, y=TP, colour = "HRboot"), size = 1)+
  geom_path(data= data$PHR, aes(x=FP, y=TP, colour = "HReq"), size = 1)+

  geom_point(data= data$TTP, aes(x=FP, y=TP, colour = "HRdiff"), size = 3)+
  geom_point(data= data$PRmeanbootdiff, aes(x=FP, y=TP, colour = "RMSTboot"), size = 3)+
  geom_point(data= data$PRMEANdiff, aes(x=FP, y=TP, colour = "RMST"), size = 3)+
  geom_point(data= data$PHRboot, aes(x=FP, y=TP, colour = "HRboot"), size = 3)+
  geom_point(data= data$PHR, aes(x=FP, y=TP, colour = "HReq"), size = 3)+
  
  geom_point(data= points[1,], aes(x=FP, y=TP, shape = "Alwayspool"), colour = "black", size = 4)+
  geom_point(data= points[2,], aes(x=FP, y=TP, shape = "Neverpool"), colour = "black", size = 4)+
  
  scale_shape_manual("", breaks = c("Alwayspool" = "Alwayspool", "Neverpool" = "Neverpool"), values = c(16,17)) +
  guides(linetype=FALSE) +
  
  guides(shape = guide_legend(override.aes = list(linetype = 0)))+

  scale_color_manual("", breaks = c("HRdiff" = "HRdiff", "RMSTboot"= "RMSTboot", "RMST" = "RMST", "HRboot" ="HRboot", "HReq" = "HReq"), values=cbPalette)+
  
  labs(colour="",linetype="",shape="")+
  
  coord_cartesian(xlim = setxaxis) + 

theme_cowplot(12)

return(plot)
}

```


#Make 1 big plot
```{r}
D11 <- makeROCplot(dat = 1, setxaxis = c(0.04,0.065), FPalwayspool = proportions$PAlwaysPool[1,4], FPneverpool = proportions$PNeverPool[1,4], TPalwayspool = proportions$PAlwaysPool[1,3], TPneverpool = proportions$PNeverPool[1,3])

D12 <- makeROCplot(dat = 2, setxaxis = c(0.04,0.1), FPalwayspool = proportions$PAlwaysPool[2,4], FPneverpool = proportions$PNeverPool[2,4], TPalwayspool = proportions$PAlwaysPool[2,3], TPneverpool = proportions$PNeverPool[2,3])

            
D13 <- makeROCplot(dat = 3, setxaxis = c(0.04,0.18), FPalwayspool = proportions$PAlwaysPool[3,4], FPneverpool = proportions$PNeverPool[3,4], TPalwayspool = proportions$PAlwaysPool[3,3], TPneverpool = proportions$PNeverPool[3,3]) #3,1

D14 <- makeROCplot(dat = 4, setxaxis = c(0.04,0.4), FPalwayspool = proportions$PAlwaysPool[4,4], FPneverpool = proportions$PNeverPool[4,4], TPalwayspool = proportions$PAlwaysPool[4,3], TPneverpool = proportions$PNeverPool[4,3]) #4,1

D21 <-  makeROCplot(dat = 5, setxaxis = c(0.04,0.19), FPalwayspool = proportions$PAlwaysPool[5,4], FPneverpool = proportions$PNeverPool[5,4], TPalwayspool = proportions$PAlwaysPool[5,3], TPneverpool = proportions$PNeverPool[5,3]) #1,2

D22 <- makeROCplot(dat = 6, setxaxis = c(0.04,0.23), FPalwayspool = proportions$PAlwaysPool[6,4], FPneverpool = proportions$PNeverPool[6,4], TPalwayspool = proportions$PAlwaysPool[6,3], TPneverpool = proportions$PNeverPool[6,3]) #2,2

D23 <- makeROCplot(dat = 7, setxaxis = c(0.04,0.3), FPalwayspool = proportions$PAlwaysPool[7,4], FPneverpool = proportions$PNeverPool[7,4], TPalwayspool = proportions$PAlwaysPool[7,3], TPneverpool = proportions$PNeverPool[7,3]) #3,2

D24 <- makeROCplot(dat = 8, setxaxis = c(0.04,0.45), FPalwayspool = proportions$PAlwaysPool[8,4], FPneverpool = proportions$PNeverPool[8,4], TPalwayspool = proportions$PAlwaysPool[8,3], TPneverpool = proportions$PNeverPool[8,3]) #4,2

arrangedfigure <- ggpubr::ggarrange(D11, D21, D12, D22, D13, D23, D14, D24, 
#         labels = c("D11", "D21", "D12", "D22", "D13", "D23", "D14", "D24"),
         labels = c(" A ", " B ","C1", "D1", "C2", "D2", "C3", "D3"),
           ncol = 2, nrow = 4, common.legend = TRUE, vjust = +0.2, hjust = -1.6, align = "hv", legend = "bottom")

annotatedfigureHR <- ggpubr::annotate_figure(arrangedfigure, 
               top = ggpubr::text_grob(expression(paste(lambda["c"],"= 776.89                                   ",lambda["c"],"= 876.89")), face = "bold", size = 20), 
              left = ggpubr::text_grob(expression(paste(sigma["s"],"=0.4                ", sigma["s"], "=0.2                ", sigma["s"], "=0.1                ", sigma["s"], "=0")), face = "bold", size = 20, rot = 90))

annotatedfigureHR

```
colnames(Npool) <- c('scalepar = 429', 'scalepar = 403')
rownames(Npool) <- c('sdrandomcluster = 0', 'sdrandomcluster = 0.1', 'sdrandomcluster = 0.2','sdrandomcluster = 0.4')

#######################################
############# RMST ####################
#######################################

#Load output from 3.FinalAnalysis
```{r}
#load("3.FinalAnalysis_output/3.ProportionsTPFPHR.Rdata")
#load("3.FinalAnalysis_output/3.DecisionsFinalAnalysesHR.Rdata")
#load("3.FinalAnalysis_output/3.Pooldecisions700HR.Rdata")

load("3.FinalAnalysis_output/3.ProportionsTPFPrmean3.Rdata") 
#load("3.FinalAnalysis_output/3.DecisionsFinalAnalyses700rmean3.Rdata")
load("3.FinalAnalysis_output/3.Pooldecisions400rmean3.Rdata") 
#load("3.FinalAnalysis_output/3.Pooldecisionsrmean3.Rdata") 
load("3.FinalAnalysis_output/3.DecisionsFinalAnalyses400rmean3.Rdata")
```

#Make a function that returns a vector with the TPs, and a vector with the FPs for the indicated dataset
```{r}
makeDF <- function(proportions, dat=1){ #example: proportions$PHR
TP <- vector()
FP <- vector()
for (i in 1:length(proportions)){
TP[i] = proportions[[i]][dat,3]
FP[i] = proportions[[i]][dat,4]
}
data <- data.frame(TP = TP, FP=FP)
return(data)
}
#plot(TP, FP)
```

#Make a function to return FP/TP plot
```{r}
cbPalette <- c("#999999", "#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#D55E00", "#CC79A7")

makeROCplot <- function(dat = 1, setxaxis, FPalwayspool, FPneverpool, TPalwayspool, TPneverpool)
{
data <- list()
data$TTP <- makeDF(proportions$PPTTP, dat = dat)
data$PRmeanbootdiff <- makeDF(proportions$PRMEANbootdiff, dat = dat)
data$PRMEANdiff <- makeDF(proportions$RMEANdiff, dat = dat)
data$PHRboot <- makeDF(proportions$PHRboot, dat = dat)
data$PHR <- makeDF(proportions$PHR, dat = dat)

points <- data.frame(
  "method" =  c("AlwaysPool", "NeverPool"),
  "FP" = c(FPalwayspool, FPneverpool),
  "TP" = c(TPalwayspool, TPneverpool))
  
plot <- ggplot(data$PHR, aes(x=FP, y=TP))+
  
  geom_path(data= data$TTP, aes(x=FP, y=TP, colour = "HRdiff"), size = 1, show.legend = FALSE)+
  geom_path(data= data$PRmeanbootdiff, aes(x=FP, y=TP, colour = "RMSTboot"), size = 1, show.legend = FALSE)+
  geom_path(data= data$PRMEANdiff, aes(x=FP, y=TP, colour = "RMST"), size = 1, show.legend = FALSE)+
  geom_path(data= data$PHRboot, aes(x=FP, y=TP, colour = "HRboot"), size = 1, show.legend = FALSE)+
  geom_path(data= data$PHR, aes(x=FP, y=TP, colour = "HReq"), size = 1, show.legend = FALSE)+

  geom_point(data= data$TTP, aes(x=FP, y=TP, colour = "HRdiff"), size = 3, show.legend = FALSE)+
  geom_point(data= data$PRmeanbootdiff, aes(x=FP, y=TP, colour = "RMSTboot"), size = 3, show.legend = FALSE)+
  geom_point(data= data$PRMEANdiff, aes(x=FP, y=TP, colour = "RMST"), size = 3, show.legend = FALSE)+
  geom_point(data= data$PHRboot, aes(x=FP, y=TP, colour = "HRboot"), size = 3, show.legend = FALSE)+
  geom_point(data= data$PHR, aes(x=FP, y=TP, colour = "HReq"), size = 3, show.legend = FALSE)+
  
  geom_point(data= points[1,], aes(x=FP, y=TP, shape = "Alwayspool"), colour = "black", size = 4, show.legend = FALSE)+
  geom_point(data= points[2,], aes(x=FP, y=TP, shape = "Neverpool"), colour = "black", size = 4, show.legend = FALSE)+
  
  scale_shape_manual("", breaks = c("Alwayspool" = "Alwayspool", "Neverpool" = "Neverpool"), values = c(16,17)) +
  guides(linetype=FALSE) +
  
  guides(shape = guide_legend(override.aes = list(linetype = 0)))+

  scale_color_manual("", breaks = c("HRdiff" = "HRdiff", "RMSTboot"= "RMSTboot", "RMST" = "RMST", "HRboot" ="HRboot", "HReq" = "HReq"), values=cbPalette)+
  
  labs(colour="",linetype="",shape="")+
  
  coord_cartesian(xlim = setxaxis) + 

theme_cowplot(12)

return(plot)
}

```


#Make 1 big plot
```{r}
D11 <- makeROCplot(dat = 1, setxaxis = c(0.045,0.07), FPalwayspool = proportions$PAlwaysPool[1,4], FPneverpool = proportions$PNeverPool[1,4], TPalwayspool = proportions$PAlwaysPool[1,3], TPneverpool = proportions$PNeverPool[1,3])

D12 <- makeROCplot(dat = 2, setxaxis = c(0.04,0.083), FPalwayspool = proportions$PAlwaysPool[2,4], FPneverpool = proportions$PNeverPool[2,4], TPalwayspool = proportions$PAlwaysPool[2,3], TPneverpool = proportions$PNeverPool[2,3])

            
D13 <- makeROCplot(dat = 3, setxaxis = c(0.04,0.14), FPalwayspool = proportions$PAlwaysPool[3,4], FPneverpool = proportions$PNeverPool[3,4], TPalwayspool = proportions$PAlwaysPool[3,3], TPneverpool = proportions$PNeverPool[3,3]) #3,1

D14 <- makeROCplot(dat = 4, setxaxis = c(0.04,0.32), FPalwayspool = proportions$PAlwaysPool[4,4], FPneverpool = proportions$PNeverPool[4,4], TPalwayspool = proportions$PAlwaysPool[4,3], TPneverpool = proportions$PNeverPool[4,3]) #4,1

D21 <-makeROCplot(dat = 5, setxaxis = c(0.04,0.18), FPalwayspool = proportions$PAlwaysPool[5,4], FPneverpool = proportions$PNeverPool[5,4], TPalwayspool = proportions$PAlwaysPool[5,3], TPneverpool = proportions$PNeverPool[5,3]) #1,2

D22 <- makeROCplot(dat = 6, setxaxis = c(0.04,0.2), FPalwayspool = proportions$PAlwaysPool[6,4], FPneverpool = proportions$PNeverPool[6,4], TPalwayspool = proportions$PAlwaysPool[6,3], TPneverpool = proportions$PNeverPool[6,3]) #2,2

D23 <- makeROCplot(dat = 7, setxaxis = c(0.04,0.25), FPalwayspool = proportions$PAlwaysPool[7,4], FPneverpool = proportions$PNeverPool[7,4], TPalwayspool = proportions$PAlwaysPool[7,3], TPneverpool = proportions$PNeverPool[7,3]) #3,2

D24 <- makeROCplot(dat = 8, setxaxis = c(0.04,0.4), FPalwayspool = proportions$PAlwaysPool[8,4], FPneverpool = proportions$PNeverPool[8,4], TPalwayspool = proportions$PAlwaysPool[8,3], TPneverpool = proportions$PNeverPool[8,3]) #4,2

arrangedfigure <- ggpubr::ggarrange(D11, D21, D12, D22, D13, D23, D14, D24, 
#         labels = c("D11", "D21", "D12", "D22", "D13", "D23", "D14", "D24"),
         labels = c(" A ", " B ","C1", "D1", "C2", "D2", "C3", "D3"),
          ncol = 2, nrow = 4, common.legend = TRUE, vjust = +0.2, hjust = -1.6, align = "hv", legend = "bottom")

annotatedfigureRMST <- ggpubr::annotate_figure(arrangedfigure, 
               top = ggpubr::text_grob(expression(paste(lambda["c"],"= 776.89                                   ",lambda["c"],"= 876.89")), face = "bold", size = 20))
```
colnames(Npool) <- c('scalepar = 429', 'scalepar = 403')
rownames(Npool) <- c('sdrandomcluster = 0', 'sdrandomcluster = 0.1', 'sdrandomcluster = 0.2','sdrandomcluster = 0.4')

#########################
##### SAMEN #############
#########################


Save plot in 4.DataVisualization_output
```{r}
arrangedfigurebeiden <- ggpubr::ggarrange(annotatedfigureHR, annotatedfigureRMST, 
          ncol = 2, nrow = 1, common.legend = TRUE, align = "hv", legend = "right")

annotatedfigurebeiden <- ggpubr::annotate_figure(arrangedfigurebeiden, 
               top = ggpubr::text_grob("HR as final analysis                                                                                  RMST as final analysis", face = "bold", size = 20))

#saveplot
ggsave("4.DataVisualization_output/1.Sim1.png", plot = annotatedfigurebeiden, width = 20, height = 10)
```

