---
title: "2.1 AlwaysPool"
author: "Joukje Willemsen"
date: "13-05-2020"
output: html_document
---

In  this docyment the "alwayspooled" controlgroups are created by combining the historical control group with the simulated control group for the scenarios referred to as A, B, E1-3 and F1-3 in the article.

Please note that:

Data11 = Scenario A

Data12 = Scenario E1

Data13 = Scenario E2

Data14 = Scenario E3

Data21 = Scenario B

Data22 = Scenario F1

Data23 = Scenario F2

Data24 = Scenario F3

#Load simulated & historical data
```{r}
load("1.DataSimulation_output/1.HcontrolShape.Rdata")
load("0.DataPreperation_output/0.Historicaldata.RData")
```

#Make function that combines the current control group with the historical group
```{r}
pool <- function (dataset) #input: Hcontrol[[1]]
{
datasetpooled <- list() #make a list called datasetpooled

for (i in 1:(length(dataset)))
  { #the minus 1 because the last 1 is the decision indicator
datasetpooled[[i]] <- data.frame(
  survivalcensored = c(dataset[[i]]$survivalcensored, Dcontrol$STIME18), 
  StatusIndicator = c(dataset[[i]]$StatusIndicator, Dcontrol$STATUS18),
  pooled = "yes")
  }

return(datasetpooled)  
}
```

#Apply function to each simulated scenario
```{r}
AlwaysPoolData <- list("Data11" = pool(Hcontrol[[1]]), 
                      "Data12" = pool(Hcontrol[[2]]),
                      "Data13" = pool(Hcontrol[[3]]),
                      "Data14" = pool(Hcontrol[[4]]),
                      "Data21" = pool(Hcontrol[[5]]), 
                      "Data22" = pool(Hcontrol[[6]]),
                      "Data23" = pool(Hcontrol[[7]]),
                      "Data24" = pool(Hcontrol[[8]]))

```

#Save datasets
```{r}
save(AlwaysPoolData, file = "2.PoolingMethods_output/2.1.AlwaysPoolDatasetShape.Rdata")
```

