---
title: "2.4 HR equivalence boot shape"
author: "Joukje Willemsen"
date: "13-05-2020"
output: html_document
---

In this document the confidence intervals of the HR test are bootstrapped for the scenarios referred to as A, B, E1-3 and F1-3 in the article.

Please note that:

Data11 = Scenario A

Data12 = Scenario E1

Data13 = Scenario E2

Data14 = Scenario E3

Data21 = Scenario B

Data22 = Scenario F1

Data23 = Scenario F2

Data24 = Scenario F3

#Load simulated & historical data
```{r}
load("1.DataSimulation_output/1.HcontrolShape.Rdata")
load("0.DataPreperation_output/0.Historicaldata.RData")
```

#Load packages
```{r}
library(survival)
library(dplyr)
```

Function to extract hazard ratios
```{r}
HR <- function (D, d) #input: Hcontrol[[1]][[1]]
{
df <-D[d,] #Indexing, needed for bootstrapping

fit <- coxph(Surv(time=survivaltime, event=event)~indicator, data = data.frame(
survivaltime=c(Dcontrol$STIME18, df$survivalcensored),
event = c(Dcontrol$STATUS18, df$StatusIndicator),
indicator=c(rep(1, 2889),rep(0, length(df$survivalcensored)))))
return(exp(fit$coefficients)) # return estimated HR
}
```

#Make function to bootstrap
```{r}
BootHR_CI <- function (df)
{
suppressWarnings({
#Bootstrap sample
bootobject<-boot::boot(data=df, statistic = HR, R=400)
#Get the bootstrapped CI
output <- boot.ci(bootobject, conf=0.95)
})
return(output$normal[2:3]) #Choose the "normal bootstrap"
}
```

Test function
```{r}
library(boot)
set.seed(100)

test <-BootHR_CI(Hcontrol[[1]][[1000]])
test
```
The confidence interval of the hazard rate ranges between 0.56 and 1.41. 

#Function that returns a matrix with all the CI's using function BootHR_CI
```{r}
BootHRmatrix <- function (list){
df <- matrix(ncol = 2, nrow = 1000) %>% data.frame() #make a matrix to store the CIs
for(i in 1:1000){ #for every simulated dataset
df[i,] <- BootHR_CI(list[[i]]) #use function BootHR_CI
}
return(df) #return the matrix with CIs
}
```

#Make a list with all the results (warning: takes a loooooong time!)
```{r}
library(boot)
set.seed(100)

#Apply function BootHRmatrix to every simulated scenario
BootCIsHR<-lapply(Hcontrol, FUN = BootHRmatrix)

#Add names to every list
names(BootCIsHR) <- c("Data11","Data12","Data13","Data14","Data21","Data22","Data23","Data24")
```

Save the bootstrapped CIs
```{r}
save(BootCIsHR, file = "2.PoolingMethods_output/2.4.BootCIsHR400Shape.Rdata")
```


