---
title: "2.6.RMST equivalence boot"
author: "Joukje Willemsen"
date: "13-05-2020"
output: html_document
---

In this document the confidence intervals of the RMST test are bootstrapped for the scenarios referred to as A, B, E1-3 and F1-3 in the article.

Please note that:

Data11 = Scenario A

Data12 = Scenario E1

Data13 = Scenario E2

Data14 = Scenario E3

Data21 = Scenario B

Data22 = Scenario F1

Data23 = Scenario F2

Data24 = Scenario F3

#Load simulated & historical data
```{r}
load("1.DataSimulation_output/1.HcontrolShape.Rdata")
load("0.DataPreperation_output/0.Historicaldata.RData")
```

#Load packages
```{r}
library(survival)
library(dplyr)
library(boot)
```


#Calculate the restricted mean survival time for the historical control
```{r}
#Make a survfit object for the historical control data
survfit_hist <- survfit(Surv(time = STIME18, event = STATUS18, type = "right") ~ 1, data = Dcontrol)

#Abstract the estimated mean from the survfit object
rmean_hist <- (survival:::survmean(survfit_hist, rmean=548) [[1]]["*rmean"])
```

#Function to bootstrap the RMST difference
```{r}
#function to extract the rmean_hist
get_rmeandiff <- function(D,d){
  E=D[d,] #Indexing, needed for bootstrapping
  #Make a survfit object for the RMST of the current controlgroup
  survfit <- survfit(Surv(time = survivalcensored, event = StatusIndicator, type = "right") ~ 1, data = E)
  #Calculate the difference in RMST
  rmean_diff <- survival:::survmean(survfit, rmean=548) [[1]]["*rmean"]-rmean_hist
  return(rmean_diff) #Return the difference
}
```

#Example
```{r}
set.seed(1234)
b = boot(data = Hcontrol[[1]][[1]], statistic=get_rmeandiff, R=400)
ci = boot.ci(b, type="basic")
ci
```
The confidence interval of the difference in RMST ranges between [-39.744, 30.000]

#Make function to bootstrap
```{r}
Bootrmean_CI <- function (df)
{
b = boot(data = df, statistic=get_rmeandiff, R=400)
ci = boot.ci(b, conf = 0.95) #obtain the bootstrapped CI

return(ci$normal[2:3])
}
```

#Function that returns a matrix with all the CI's using function BootHR_CI
```{r}
Bootrmean_matrix <- function (list){
df <- matrix(ncol = 2, nrow = 1000) %>% data.frame() #make a dataframe
for(i in 1:1000){ #for every simulated sample
df[i,] <- Bootrmean_CI(list[[i]]) #store the bootstrapped CI in the dataframe
}
return(df)
}
```

Make a list with all the results (Warning, this takes a long time!!!!)
```{r}
BootCIsRMEAN<-lapply(Hcontrol, FUN = Bootrmean_matrix)

names(BootCIsRMEAN) <- c("Data11","Data12","Data13","Data14","Data21","Data22","Data23","Data24")
```


#Save CIs
```{r}
save(BootCIsRMEAN, file = "2.PoolingMethods_output/2.6.Boot_CIsRMEANShapeSNEL.Rdata")
```

